\chapter{Competitor Analysis}
With the rising popularity and prominence of artificial intelligence, it is expected
that it could be used to tackle obstacles such as disabilities. However, the market
for blindness-assisting technologies remains fairly unsaturated. Nevertheless, 
the few noteworthy products listed below have a relatively good track record and are rapidly evolving.
Despite this, there are some gaping holes still left unfilled, which BlindSight could
provide a solution for. \\

\section{Competitor 1: Envision}
\textit{Envision website: https://letsenvision.com/} \\
\\
A product with such a wide array of features such as Envision will surely be a 
worthy match to BlindSight. Their business offers worldwide shipping for their three
models. Envision's glasses have a slick, lightweight design making them suitable
for a full day's usage. The features of the Envision glasses vary based on the model: \\
\\
\begin{itemize}
    \item Envision Glasses Read Edition: Instant Text, Scan Text, Batch Scan (€2499 + Tax)
    \item Envision Glasses Home Edition: Instant Text, Scan Text, Batch Scan, Call an Ally, Call Aira, Describe Scene, Detect Light, Recognize Cash, Detect Colors, Find People, Find Objects, Teach a Face and Explore (€3499 + Tax)
    \item Envision Glasses Professional Edition: Instant Text, Scan Text, Batch Scan, Call an Ally, Call Aira, Describe Scene, Detect Light, Recognize Cash, Detect Colors, Find People, Find Objects, Teach a Face and Explore (€4599 + Tax) 
\end{itemize}
The downside of the Envision Glasses is their premium price. The base model, the Envision Reading Edition, comes out
to a hefty €2499 without tax. Being a base model, the Envision Reading Edition is missing many key features
of the more expensive models; it only contains features dealing with interpreting scanned text. The subsequent model,
the Envision Home Edition, possesses all the features, but it is €1000 more expensive to the Envision Reading Edition.
The Envision Professional Edition, which as a reminder has the exact same features as the Envision Home Edition,
will set back a buyer northwards of €4599. The concern with high prices such as these of the Envision models is that they price out
many visually impaired customers out of the market. Moreover, they only come with a year's worth of warranty and for such 
a pricey product many potential buyers could easily be deterred by the limited coverage period. A year's worth of warranty might 
not provide adequate protection, especially for high-value items that could require more extensive coverage over 
a longer period. As for the Envision Subscription Edition, it is only available in the contiguous United States, making it 
inaccessible to potential consumers on the international market. Furthermore, despite
the rental model saving the consumer money in the short-run, over the long-run the Envision Subscription edition could
easily out-price the Home Edition and the Professional Edition. Over a two-year span, the Envision Subscription edition will have
cost the consumer €3600 which would then increase to €5400 over a 3-year span. While there could be instances
where one's blindness could be temporary, for many the disability will last for their entire lives. Hence, it is important
that they have available an inexpensive alternative such as BlindSight that will serve to help them without putting a strain
on their wallets.\\
\\
Despite Envision's head start in the market, they are focused on providing a premium product which leaves
the door open to an alternative that would concentrate on making such technology more accessible to the international
market. The success of Envision could serve as a blueprint to BlindSight as they are a proof-of-concept
that smart glasses could have a substantial impact on the lives of those living with visual impairments. Moreover,
Envision's products rely on voice feedback to the user which is much slower than the haptic feedback that the 
BlindSight bracelets would provide on top of voice warnings. BlindSight will have all the functionality of Envision's most
premium products in addition to a better danger warning system during navigation, all the while providing a product that
is ten times more affordable than Envision's base model. \\
\\
\newpage
\section{Competitor 2: Be My Eyes}
\textit{Be My Eyes website: https://www.bemyeyes.com/ } \\
\\
Be My Eyes is an app that helps connect visually impaired people with volunteers,
who can provide aid in discerning what is in front of the blind person. The app works is by establishing a video
call between the visually impaired individual and the volunteer. The volunteer can then describe what he sees in the 
video to the visually impaired person. \\
With the advent of ChatGPT-4, Be My Eyes has incorporated the AI into its product. Now, users can take a picture
and record a message which is consequently transcribed to text and sent over to ChatGPT for analysis. \\
\\
Be My Eyes is a rather versatile tool considering with the added bonus that it is free of charge to use. However, a drawback is that in order
for the video functionality to work, a volunteer is required to be online which renders the feature unreliable. As for the 
ChatGPT-powered AI image detection, that is a rather arduous process for the user, who besides first opening the app, must then
take a picture, record a message and only then can they send it for processing. \\
\\
BlindSight's features an upgrade to the ones Be My Eyes currently has. Furthermore, BlindSight understands the importance
that conducting tasks independently has on one's perception of self-worth. Hence, all of BlindSight's functionalities
will be entirely reliant on AI which will always be readily available, as opposed to the unreliable factor of whether
there are any volunteers available to help. \\
\\
The main advantage that Be My Eyes has over BlindSight is that it is free to use. However, BlindSight's many other 
utilities justify its subscription fee as the features will unlock new possibilities for the users which could
not be accomplished using Be My Eyes. \\
\\
\newpage
\section{Competitor 3: .lumen}
\textit{.lumen website: https://www.dotlumen.com/ } \\
\\
A new competitor to the market, .lumen still does not have a product available. Their main area of focus is
helping the visually impaired navigate through AI depth detection and image recognition software. Unfortunately,
not much is known about the company or how much they will charge for their product. \\
\\
The scarcity of information regarding the product, makes any weakness analysis purely based on speculation. It is reasonable
to assume that users will be notified of any dangers by a voice assistant embedded in the headset. This can prove to be rather 
ineffective if the danger is fast-approaching and the user needs to react quickly. Furthermore, the headset itself looks fairly heavy
and there exists a possible concern that a user will not be able to wear it for extended periods of time due to the eventual exhaustion on the 
neck area. \\
\\
The company has not entered the marker yet, giving BlindSight an ample chance to catch up. Their product will surely require powerful 
processors in order to utilize the AI tool set locally. This implies that the product will most likely have a premium price, making it
inaccessible to poorer consumers. Rather than fitting all the technology into one bulky and awkward headset, BlindSight will utilize the 
user's phone and the optional extension set to accomplish similar functionality to .lumen, all the meanwhile providing a more lightweight 
solution. \\
\\
The company has had time to research and develop their product giving them a head start over BlindSight. The
possibility that their AI will work offline and will be able to analyze the video recordings faster is an 
area that BlindSight could potentially rival .lumen in by hosting a less powerful AI into the mobile app, for 
cases where the main server is not easily reachable. \\
