\chapter{Distribution Strategy}

\section{Philosophy}
BlindSight aims to empower visually impaired individuals by providing a relatively affordable
technology, through which said individuals could accomplish their daily tasks in an easier and more
independent manner.

\section{Product Development}
BlindSight will develop a minimum-viable product sometime in the second
quarter of 2024. This will comprise a mobile application which will
utilize the phone's capabilities to record video, to communicate with the AI model
and to relay the instructions back to the user. \\
\\
In the second half on 2024, after getting feedback
on the prototype, BlindSight will focus on developing the extension set necessary to 
elevate the company above the competition. The company will have a fully operational
model sometime in 2025.

\section{Distribution}
BlindSight will get in touch with optometry and ophthalmology clinics in order
to test the progress with individuals who are visually impaired.
Once the minimum-viable product is ready, BlindSight will rely on optometrists
recommending the app to the target market. At this stage the app will be in beta, and it will be free
for the users. The cooperating optometrists will receive a special affiliate code which will grant them
15\% of the subscription fees paid by any users that use the said code. \\
\\
At the same time, BlindSight will seek to be an official partner of non-profit organizations
seeking to provide aid to the visually impaired. BlindSight will offer package deals
to such organizations and in turn the product will establish itself as the accessible,
go-to product for assistive technologies for the blind. One possible such package could be a 3-month free
subscription to the mobile app once it reaches the production stage. \\
\\
Additionally, once the extension set has become available for purchase BlindSight could rent out an amount of 
extension sets to these non-profits based on the amount of new subscriptions these organizations attract.

\section{Sales}
BlindSight will initially focus on affordable monthly subscription fees to finance further development of the extension set. 
The strategy here is to evaluate the interest of the market for a more affordable solution, all the while minimizing
initial capital needed to launch the company off the ground.
A similar business model has been proven to be effective by Envision, however
in order to reel more users in, BlindSight's subscription will be more affordable (approximately €5 per month). \\
\\
Moreover, BlindSight's extension set will sell 
for €499 (a substantially lower price than Envision's base model price of €2499 pre-tax).

\section{Goals}
\begin{enumerate}
    \item Release the mobile app as beta to users through our affiliations by the end of the second quarter of 2024.
    \item Develop a prototype of the extension set by the end of the third quarter of 2024.
    \item Complete transition of mobile app to production and begin monetization by the end of 2024.
    \item Release the extension set for purchase at the end of the 1st quarter of 2025.
\end{enumerate}
